Preprocessing: filtering

### 2022-09-21 analysis/preprosessor/predata/filtering.Rmd
update predata
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# read a text file for ideal performance
dt_ideal <- read.table(here("ideal.txt"))
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))

# create a list of data file names
lf <- list.files(here("raw_data"), pattern = "txt")

# create raw_data - merge all data files into one
raw_data <- data.table()
for (i in 1:length(lf)){
  data_i <- fread(file.path(here("raw_data"), lf[i]), header = F, sep = " ", dec = ".")
  raw_data <- rbind(raw_data, data_i)
}

@@

# onset and offset for experimental session
dt_onset <- dt_all[Key_OnOff == 1 & Session == "experiment"]
dt_offset <- dt_all[Key_OnOff == 0 & Session == "experiment"]
```

@@

```{r sub-onset, include = FALSE, eval = FALSE}
error_sub_onset <- dt_error_onset[startsWith(Reason, "Substituted")]

dt_correct_onset_4 <- data.table()
for (row in 1:nrow(error_sub_onset)){
  current <- dt_onset[SubNr == error_sub_onset$SubNr[row] & TrialNr == error_sub_onset$TrialNr[row]]
  decision = 2 
  correction = 0 # # of correction for reporting stats
  while (decision == 2){
    print(sprintf("SubNr: %s, TrialNr: %s", unique(current$SubNr), unique(current$TrialNr)))
    print("----- First check -----")
    current <- edit(current, dt_ideal)
    print("----- Correction check -----")
    edit(current, dt_ideal)
    decision <- menu(c("y", "n", "other"), title = "Save the current data? (to continue, enter 'n')")
    if (decision == 1){
      correction = correction + 1
      error_sub_onset$CorrectionNr[row] <- correction
      dt_correct_onset_4 <- rbind(dt_correct_onset_4, current[, -c(5:6)])
    } else if (decision == 3) {
      error_sub_onset$CorrectionNr[row] <- readline(prompt = "Reason?: ")
    } else if (decision == 2){
      correction = correction + 1
      print("----- Continue correction -----")
    }
  }
}

@@

- SubNr: 12, TrialNr: 13

@@

# remove the first error
current_1 <- edit(current_1, dt_ideal)
current_1$Ideal <- dt_ideal$Pitch
graph(current_1)

# corrected the second error (substituted note)
current_1 <- edit(current_1, dt_ideal)
graph(current_1)

error_ind_onset$CorrectionNr[1] <- 2
```

- SubNr: 10, TrialNr: 10

```{r, include = FALSE, eval = FALSE}
current_2 <- dt_onset[SubNr == error_ind_onset$SubNr[2] & TrialNr == error_ind_onset$TrialNr[2]]

# insert one note
current_2 <- insert_na(current_2, dt_ideal)
current_2$RowNr <- c(1:nrow(current_2))
current_2$Ideal <- dt_ideal$Pitch
graph(current_2)

# insert one note
current_2 <- edit(current_2, dt_ideal)
current_2$RowNr <- 1:nrow(current_2)
current_2$Ideal <- cc(dt_ideal$Pitch, rep(NA, abs(nrow(current_2) - nrow(dt_ideal))))
graph(current_2)

# remove one extra note
current_2 <- edit(current_2, dt_ideal)
current_2$Ideal <- dt_ideal$Pitch
graph(current_2)

error_ind_onset$CorrectionNr[2] <- 3
```

- SubNr: 6, TrialNr: 2

```{r, include = FALSE, eval = FALSE}
current_3 <- dt_onset[SubNr == error_ind_onset$SubNr[3] & TrialNr == error_ind_onset$TrialNr[3]]
current_3$RowNr <- c(1:nrow(current_3))
current_3$Ideal <- dt_ideal$Pitch
graph(current_3)

# remove the first error
current_3 <- edit(current_3, dt_ideal)

# insert one note
current_3 <- insert_na(current_3, dt_ideal)
current_3$Ideal <- dt_ideal$Pitch
graph(current_3)

error_ind_onset$CorrectionNr[3] <- 2
```

- SubNr: 6, TrialNr: 12

```{r, include = FALSE, eval = FALSE}
current_4 <- dt_onset[SubNr == error_ind_onset$SubNr[4] & TrialNr == error_ind_onset$TrialNr[4]]
current_4$RowNr <- c(1:nrow(current_4))
current_4$Ideal <- dt_ideal$Pitch
graph(current_4)

# insert one skipped note
current_4 <- edit(current_4, dt_ideal)
current_4$RowNr <- 1:nrow(current_4)
current_4$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_4) - nrow(dt_ideal))))
graph(current_4)

# remove one extra note
current_4 <- edit(current_4, dt_ideal)
current_4$RowNr <- c(1:nrow(current_4))
current_4$Ideal <- dt_ideal$Pitch
graph(current_4)

error_ind_onset$CorrectionNr[4] <- 2
```

- SubNr: 8, TrialNr: 6

```{r, include = FALSE, eval = FALSE}
current_5 <- dt_onset[SubNr == error_ind_onset$SubNr[5] & TrialNr == error_ind_onset$TrialNr[5]]
current_5$RowNr <- c(1:nrow(current_5))
current_5$Ideal <- dt_ideal$Pitch
graph(current_5)

# remove one wrong note
current_5 <- edit(current_5, dt_ideal)

# insert one note
current_5 <- insert_na(current_5, dt_ideal)
current_5$RowNr <- c(1:nrow(current_5))
current_5$Ideal <- dt_ideal$Pitch
graph(current_5)

error_ind_onset$CorrectionNr[5] <- 2
```

- SubNr: 8, TrialNr: 10

```{r, include = FALSE, eval = FALSE}
current_6 <- dt_onset[SubNr == error_ind_onset$SubNr[6] & TrialNr == error_ind_onset$TrialNr[6]]
current_6$RowNr <- c(1:nrow(current_6))
current_6$Ideal <- dt_ideal$Pitch
graph(current_6)

# remove one extra note
current_6 <- edit(current_6, dt_ideal)

# insert one note
current_6 <- insert_na(current_6, dt_ideal)
current_6$RowNr <- c(1:nrow(current_6))
current_6$Ideal <- dt_ideal$Pitch
graph(current_6)

error_ind_onset$CorrectionNr[6] <- 2
```

- SubNr: 13, TrialNr: 1

```{r, include = FALSE, eval = FALSE}
current_7 <- dt_onset[SubNr == error_ind_onset$SubNr[7] & TrialNr == error_ind_onset$TrialNr[7]]
current_7$RowNr <- c(1:nrow(current_7))
current_7$Ideal <- dt_ideal$Pitch
graph(current_7)

# insert one note
current_7 <- edit(current_7, dt_ideal)
current_7$RowNr <- 1:nrow(current_7)
current_7$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_7) - nrow(dt_ideal))))
graph(current_7)

# remove one note
current_7 <- edit(current_7, dt_ideal)
current_7$RowNr <- c(1:nrow(current_7))
current_7$Ideal <- dt_ideal$Pitch
graph(current_7)

error_ind_onset$CorrectionNr[7] <- 2
```

```{r, include = FALSE, eval = FALSE}
dt_correct_onset_5 <- rbind(current_1, current_2, current_3, current_4, current_5, current_6, current_7)
dt_correct_onset_5 <- dt_correct_onset_5[, -c(5:6)]

@@

- SubNr: 12, TrialNr: 13

```{r, include = FALSE, eval = FALSE}
current_1 <- dt_onset[SubNr == error_ind_offset$SubNr[1] & TrialNr == error_ind_offset$TrialNr[1]]
current_1$RowNr <- c(1:nrow(current_1))
current_1$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_1) - nrow(dt_ideal))))
graph(current_1)

@@

# corrected the second error (substituted note)
current_1 <- edit(current_1, dt_ideal)
graph(current_1)

error_ind_offset$CorrectionNr[1] <- 2
```

- SubNr: 17, TrialNr: 7

@@

# correct two notes
current_2 <- edit(current_2, dt_ideal)
graph(current_2)

# remove one note
current_2 <- edit(current_2, dt_ideal)
current_2$Ideal <- dt_ideal$Pitch
graph(current_2)

error_ind_offset$CorrectionNr[2] <- 3
```

- SubNr: 4, TrialNr: 4

```{r, include = FALSE, eval = FALSE}
current_3 <- dt_offset[SubNr == error_ind_offset$SubNr[3] & TrialNr == error_ind_offset$TrialNr[3]]
current_3$RowNr <- c(1:nrow(current_3))
current_3$Ideal <- dt_ideal$Pitch[-c(71, 72)]
graph(current_3)

# correct two notes
current_3 <- edit(current_3, dt_ideal[-c(71, 72),])
current_3$RowNr <- c(1:nrow(current_3))
current_3$Ideal <- dt_ideal$Pitch[-c(71, 72)]
graph(current_3)

# insert one notes
current_3 <- edit(current_3, dt_ideal[-c(71, 72),])
current_3$RowNr <- c(1:nrow(current_3))
current_3$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_3)

# correct two notes
current_3 <- edit(current_3, dt_ideal[-c(72),])
current_3$RowNr <- c(1:nrow(current_3))
current_3$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_3)

# insert one note
current_3 <- insert_na(current_3, dt_ideal)
current_3$RowNr <- c(1:nrow(current_3))
current_3$Ideal <- dt_ideal$Pitch
graph(current_3)

error_ind_offset$CorrectionNr[3] <- 6
```

- SubNr: 4, TrialNr: 4

```{r, include = FALSE, eval = FALSE}
current_4 <- dt_offset[SubNr == error_ind_offset$SubNr[4] & TrialNr == error_ind_offset$TrialNr[4]]
current_4$RowNr <- c(1:nrow(current_4))
current_4$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_4)

# correct two notes
current_4 <- edit(current_4, dt_ideal[-c(72),])
current_4$RowNr <- c(1:nrow(current_4))
current_4$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_4)

# insert one note
current_4 <- insert_na(current_4, dt_ideal)
current_4$RowNr <- c(1:nrow(current_4))
current_4$Ideal <- dt_ideal$Pitch
graph(current_4)

error_ind_offset$CorrectionNr[4] <- 3
```

- SubNr: 7, TrialNr: 11

```{r, include = FALSE, eval = FALSE}
current_5 <- dt_offset[SubNr == error_ind_offset$SubNr[5] & TrialNr == error_ind_offset$TrialNr[5]]
current_5$RowNr <- c(1:nrow(current_5))
current_5$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_5)

# correct two notes
current_5 <- edit(current_5, dt_ideal[-c(72),])
current_5$RowNr <- c(1:nrow(current_5))
current_5$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_5)

# insert one note
current_5 <- insert_na(current_5, dt_ideal)
current_5$RowNr <- c(1:nrow(current_5))
current_5$Ideal <- dt_ideal$Pitch
graph(current_5)

error_ind_offset$CorrectionNr[5] <- 3
```

- SubNr: 10, TrialNr: 10

```{r, include = FALSE, eval = FALSE}
current_6 <- dt_offset[SubNr == error_ind_offset$SubNr[6] & TrialNr == error_ind_offset$TrialNr[6]]
current_6$RowNr <- c(1:nrow(current_6))
current_6$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_6)

# insert one note
current_6 <- insert_na(current_6, dt_ideal)
current_6$RowNr <- c(1:nrow(current_6))
current_6$Ideal <- dt_ideal$Pitch
graph(current_6)

# insert one note
current_6 <- edit(current_6, dt_ideal)
current_6$RowNr <- c(1:nrow(current_6))
current_6$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_6) - nrow(dt_ideal))))
graph(current_6)

# remove one note
current_6 <- edit(current_6, dt_ideal)
current_6$RowNr <- c(1:nrow(current_6))
current_6$Ideal <- dt_ideal$Pitch
graph(current_6)

error_ind_offset$CorrectionNr[6] <- 3
```

- SubNr: 17, TrialNr: 1

```{r, include = FALSE, eval = FALSE}
current_7 <- dt_offset[SubNr == error_ind_offset$SubNr[7] & TrialNr == error_ind_offset$TrialNr[7]]
current_7$RowNr <- c(1:nrow(current_7))
current_7$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_7)

# insert one note
current_7 <- insert_na(current_7, dt_ideal)
current_7$RowNr <- c(1:nrow(current_7))
current_7$Ideal <- dt_ideal$Pitch
graph(current_7)

# correct four notes
current_7 <- edit(current_7, dt_ideal)
current_7$RowNr <- c(1:nrow(current_7))
current_7$Ideal <- dt_ideal$Pitch
graph(current_7)

error_ind_offset$CorrectionNr[7] <- 5
```

- SubNr: 17, TrialNr: 6

```{r, include = FALSE, eval = FALSE}
current_8 <- dt_offset[SubNr == error_ind_offset$SubNr[8] & TrialNr == error_ind_offset$TrialNr[8]]
current_8$RowNr <- c(1:nrow(current_8))
current_8$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_8)

# correct two notes
current_8 <- edit(current_8, dt_ideal[-c(72),])
current_8$RowNr <- c(1:nrow(current_8))
current_8$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_8)

# insert one note
current_8 <- insert_na(current_8, dt_ideal)
current_8$RowNr <- c(1:nrow(current_8))
current_8$Ideal <- dt_ideal$Pitch
graph(current_8)

error_ind_offset$CorrectionNr[8] <- 3
```

- SubNr: 17, TrialNr: 14

```{r, include = FALSE, eval = FALSE}
current_9 <- dt_offset[SubNr == error_ind_offset$SubNr[9] & TrialNr == error_ind_offset$TrialNr[9]]
current_9$RowNr <- c(1:nrow(current_9))
current_9$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_9)

# correct two notes
current_9 <- edit(current_9, dt_ideal[-c(72),])
current_9$RowNr <- c(1:nrow(current_9))
current_9$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_9)

# insert one note
current_9 <- insert_na(current_9, dt_ideal)
current_9$RowNr <- c(1:nrow(current_9))
current_9$Ideal <- dt_ideal$Pitch
graph(current_9)

error_ind_offset$CorrectionNr[9] <- 3
```

- SubNr: 20, TrialNr: 1

```{r, include = FALSE, eval = FALSE}
current_10 <- dt_offset[SubNr == error_ind_offset$SubNr[10] & TrialNr == error_ind_offset$TrialNr[10]]
current_10$RowNr <- c(1:nrow(current_10))
current_10$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_10)

# correct two notes
current_10 <- edit(current_10, dt_ideal[-c(72),])
current_10$RowNr <- c(1:nrow(current_10))
current_10$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_10)

# insert one note
current_10 <- insert_na(current_10, dt_ideal)
current_10$RowNr <- c(1:nrow(current_10))
current_10$Ideal <- dt_ideal$Pitch
graph(current_10)

error_ind_offset$CorrectionNr[10] <- 3
```

- SubNr: 6, TrialNr: 2

```{r, include = FALSE, eval = FALSE}
current_11 <- dt_offset[SubNr == error_ind_offset$SubNr[11] & TrialNr == error_ind_offset$TrialNr[11]]
current_11$RowNr <- c(1:nrow(current_11))
current_11$Ideal <- dt_ideal$Pitch
graph(current_11)

# remove one note
current_11 <- edit(current_11, dt_ideal)
current_11$RowNr <- c(1:nrow(current_11))
current_11$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_11)

# insert one note
current_11 <- insert_na(current_11, dt_ideal)
current_11$RowNr <- c(1:nrow(current_11))
current_11$Ideal <- dt_ideal$Pitch
graph(current_11)

error_ind_offset$CorrectionNr[11] <- 2
```

- SubNr: 6, TrialNr: 12

```{r, include = FALSE, eval = FALSE}
current_12 <- dt_offset[SubNr == error_ind_offset$SubNr[12] & TrialNr == error_ind_offset$TrialNr[12]]
current_12$RowNr <- c(1:nrow(current_12))
current_12$Ideal <- dt_ideal$Pitch
graph(current_12)

# insert one note
current_12 <- edit(current_12, dt_ideal)
current_12$RowNr <- c(1:nrow(current_12))
current_12$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_12) - nrow(dt_ideal))))
graph(current_12)

# remove one note
current_12 <- edit(current_12, dt_ideal)
current_12$RowNr <- c(1:nrow(current_12))
current_12$Ideal <- dt_ideal$Pitch
graph(current_12)

error_ind_offset$CorrectionNr[12] <- 2
```

- SubNr: 8, TrialNr: 6

```{r, include = FALSE, eval = FALSE}
current_13 <- dt_offset[SubNr == error_ind_offset$SubNr[13] & TrialNr == error_ind_offset$TrialNr[13]]
current_13$RowNr <- c(1:nrow(current_13))
current_13$Ideal <- dt_ideal$Pitch
graph(current_13)

# remove one note
current_13 <- edit(current_13, dt_ideal)
current_13$RowNr <- c(1:nrow(current_13))
current_13$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_13)

# insert one note
current_13 <- insert_na(current_13, dt_ideal)
current_13$RowNr <- c(1:nrow(current_13))
current_13$Ideal <- dt_ideal$Pitch
graph(current_13)

error_ind_offset$CorrectionNr[13] <- 2
```

- SubNr: 8, TrialNr: 10

```{r, include = FALSE, eval = FALSE}
current_14 <- dt_offset[SubNr == error_ind_offset$SubNr[14] & TrialNr == error_ind_offset$TrialNr[14]]
current_14$RowNr <- c(1:nrow(current_14))
current_14$Ideal <- dt_ideal$Pitch
graph(current_14)

# remove one note
current_14 <- edit(current_14, dt_ideal)
current_14$RowNr <- c(1:nrow(current_14))
current_14$Ideal <- dt_ideal$Pitch[-c(72)]
graph(current_14)

# insert one note
current_14 <- insert_na(current_14, dt_ideal)
current_14$RowNr <- c(1:nrow(current_14))
current_14$Ideal <- dt_ideal$Pitch
graph(current_14)

error_ind_offset$CorrectionNr[14] <- 2
```

- SubNr: 13, TrialNr: 1

```{r, include = FALSE, eval = FALSE}
current_15 <- dt_offset[SubNr == error_ind_offset$SubNr[15] & TrialNr == error_ind_offset$TrialNr[15]]
current_15$RowNr <- c(1:nrow(current_15))
current_15$Ideal <- dt_ideal$Pitch
graph(current_15)

# insert one note
current_15 <- edit(current_15, dt_ideal)
current_15$RowNr <- c(1:nrow(current_15))
current_15$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_15) - nrow(dt_ideal))))
graph(current_15)

# remove one note
current_15 <- edit(current_15, dt_ideal)
current_15$RowNr <- c(1:nrow(current_15))
current_15$Ideal <- dt_ideal$Pitch
graph(current_15)

error_ind_offset$CorrectionNr[15] <- 2
```

```{r, include = FALSE, eval = FALSE}
dt_correct_offset_5 <- rbind(current_1, current_2, current_3, current_4, current_5, current_6, current_7, current_8, current_9, current_10, current_11, current_12, current_13, current_14, current_15)
dt_correct_offset_5 <- dt_correct_offset_5[, -c(5:6)]

@@

# read a text file for ideal performance
dt_ideal <- read.table(here("ideal.txt"))
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))

>>>>

# read a text file for ideal performance
dt_ideal <- read.table(here("../ideal.txt"))
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))

# create a list of data file names
lf <- list.files(here("../raw_data"), pattern = "txt")

# create raw_data - merge all data files into one
raw_data <- data.table()
for (i in 1:length(lf)){
  data_i <- fread(file.path(here("../raw_data"), lf[i]), header = F, sep = " ", dec = ".")
  raw_data <- rbind(raw_data, data_i)
}

@@

# onset and offset for experimental session
dt_onset <- dt_all[Key_OnOff == 1 & Session == "pre"]
dt_offset <- dt_all[Key_OnOff == 0 & Session == "pre"]
```

@@

```{r sub-onset, include = FALSE, eval = FALSE}
error_sub_onset <- dt_error_onset[startsWith(Reason, "Substituted")]
dt_correct_onset_4 <- data.table()

@@

- SubNr: 20, TrialNr: 2

@@

# remove the first error
current_1 <- edit(current_1, dt_ideal)
current_1$RowNr <- c(1:nrow(current_1))
current_1$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_1) - nrow(dt_ideal))))
graph(current_1)

# remove the second error
current_1 <- edit(current_1, dt_ideal)
current_1$RowNr <- c(1:nrow(current_1))
current_1$Ideal <- dt_ideal$Pitch
graph(current_1)

# correct two notes
current_1 <- edit(current_1, dt_ideal)
current_1$RowNr <- c(1:nrow(current_1))
current_1$Ideal <- dt_ideal$Pitch
graph(current_1)

error_ind_onset$CorrectionNr[1] <- 4
```

- SubNr: 20, TrialNr: 1
Excluded because the participant stopped playing in the middle.

```{r, include = FALSE, eval = FALSE}
error_ind_onset$CorrectionNr[2] <- "Excluded"
```

```{r, include = FALSE, eval = FALSE}
dt_correct_onset_5 <- current_1
dt_correct_onset_5 <- dt_correct_onset_5[, -c(5:6)]

@@

- SubNr: 11, TrialNr: 1

```{r, include = FALSE, eval = FALSE}
current_1 <- dt_offset[SubNr == error_ind_offset$SubNr[1] & TrialNr == error_ind_offset$TrialNr[1]]
current_1$RowNr <- c(1:nrow(current_1))
current_1$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_1) - nrow(dt_ideal))))
graph(current_1)

# correct two notes
current_1 <- edit(current_1, dt_ideal)
current_1$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_1) - nrow(dt_ideal))))
graph(current_1)

# remove one note
current_1 <- edit(current_1, dt_ideal)
current_1$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_1) - nrow(dt_ideal))))
graph(current_1)

@@

error_ind_offset$CorrectionNr[1] <- 4
```

- SubNr: 20, TrialNr: 2

@@

# remove one note
current_2 <- edit(current_2, dt_ideal)
current_2$RowNr <- c(1:nrow(current_2))
current_2$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_2) - nrow(dt_ideal))))
graph(current_2)

# remove one note
current_2 <- edit(current_2, dt_ideal)
current_2$RowNr <- c(1:nrow(current_2))
current_2$Ideal <- dt_ideal$Pitch
graph(current_2)

# correct two notes
current_2 <- edit(current_2, dt_ideal)
current_2$RowNr <- c(1:nrow(current_2))
current_2$Ideal <- dt_ideal$Pitch
graph(current_2)

error_ind_offset$CorrectionNr[2] <- 4
```

- SubNr: 20, TrialNr: 1
Excluded because the participant stopped playing in the middle.

```{r, include = FALSE, eval = FALSE}
error_ind_offset$CorrectionNr[3] <- "Excluded"
```

```{r, include = FALSE, eval = FALSE}
dt_correct_offset_5 <- rbind(current_1, current_2)
dt_correct_offset_5 <- dt_correct_offset_5[, -c(5:6)]

@@

# read a text file for ideal performance
dt_ideal <- read.table(here("../ideal.txt"))
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))
